---
title: "Data Quality Control"
author: "Irfan Khan"
output: html_document
---

R features reserved words representing different cases:

NA        — "Not available"     Missing value
NaN       — "Not a number"      Invalid computation
(-)lnf    — Infinite value      Mostly invalid computation
NULL      — Empty object

Special functions to find such values in a dataset:
is.na() / is.nan() / is.finite() / is.null()
duplicated values: duolicated()

Outliers are data points that are significantly different
than the entire population.

### missing values
```{r}
is.na(c(1,2,4,NA))
```
### if the values are number
```{r}
is.finite(c(5,7,9,NaN,NA))
```
###Duplicate value
```{r}
duplicated(c(1.1,2,2,4,8.88,8.88))
```
###Example
```{r}
setwd(".")
data1 <- read.csv("E:/DATA_SET_1.csv", row.names = 1)
```
and create an index pointing out individuals of age 105 years
```{r}
idx <- which(data1$Age == 105)
data1[idx,]
```
we can iterate over colunns of our dataset and test if there are any NaN contained
```{r}
for(i in 1:ncol(data1))
{
  if(any(is.nan(data1 [,i])))
  {
    cat('There are ', length(is.nan(data1[,i])), 'NaNs in column ', colnames(data1)[i],'\n')
  }else
  {
  cat('There are no NaNs in column ', colnames(data1)[i],'\n')
  }
}
```    

